Appendix 3: Estimating species interactions

### 2015-10-29 Harris_2015/manuscript-materials/draft.Rmd
almost done

Whereas Figure 3 summarizes the accuracy of each model's point estimates, Figure
4 compares the inferential value of the Markov network versus the null model.
When the "true" $\beta$ coefficient is near zero, the Markov network's 95%
confidence intervals usually include zero (but not quite 95% of the time), and
it is rare for the model to confidently attribute the wrong sign to a
coefficient (Figure 4A). The null model, by contrast, typically rejects the null
hypothesis at the $p=0.05$ level regardless of the underlying parameters, and
the sign of its $Z$-scores is not a reliable indicator of the interaction's
actual sign.

>>>>

Whereas Figure 3 summarizes the accuracy of each model's point estimates, Figure
4 compares the inferential value of the Markov network versus the null model.
When the "true" $\beta$ coefficient is near zero, the Markov network's 95%
confidence intervals usually include zero (but not quite 95% of the time), and
it is rare for the model to confidently attribute the wrong sign to a
coefficient (Figure 4A). The Pairs software, by contrast, typically rejects the null
hypothesis at the $p=0.05$ level regardless of the underlying parameters, and
the sign of its $Z$-scores is not a reliable indicator of the interaction's
actual sign (Figure 4B).
